Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-17 manuscript.Rmd
Edit to footnote 4

In order to distinguish between these possibilities, we can define what a “meaningful effect” (SESOI) would be and use it as the bounds for an equivalence test. If grades for this test were set at every `r printnum(sesoi * 100)`\% increase in correct answers (F = 0% to 6.25% ... A+ = 93.75% to 100%) we could decide that we are only interested in test differences that correspond to an increase or decrease of at least 1 grade point. Thus, our SESOI becomes a difference in raw scores of `r printnum(sesoi * 100)`\%, or `r printnum(sesoi, digits = 4)`. We can then perform the TOST procedure for a two-sample Welch’s *t*-test, using $\pm$ the SESOI of `r printnum(sesoi, digits = 4)` as the equivalence bounds ($\Delta$).
The TOST is non-significant, $t(`r printnum(Moon$TOST_df)`) = `r printnum(min(abs(c(Moon$TOST_t1, Moon$TOST_t2))))`$, $p = `r printp(max(Moon$TOST_p1, Moon$TOST_p2))`$ (Figure 2A). Thus, we cannot reject a true effect as large or larger than 6.25%.^[In this example, the bounds of the TOST were based on a raw effect of 6.25%. We could have converted this raw effect into a standardized effect (Cohen's $d$) for the current sample, and we would have gotten the exact same result ($\Delta = \pm `r printnum(0.0625 / sqrt((sd.asian^2 + sd.control^2) / 2))`)$. Since this is a replication of a previous study, we could also have chosen to calculate the Cohen's $d$ that corresponds to the raw SESOI in the *original* study, and used this as the bounds for the replication. Now we would no longer be answering a question about a raw effect independent of the samples, but rather if the replication can reject standardized effects larger than a certain standardized effect in the original. Since the standard deviations of the original study were larger than in the replication in this case, Cohen's $d$ (and thus the bounds) would be narrower ($\Delta = \pm `r printnum(sesoi / sqrt((sd.asian^2 + sd.control^2) / 2))`)$.] When results are neither statistically different from zero nor statistically equivalent, there is insufficient data to draw conclusions. Further studies are needed, which can be analyzed using a (small-scale) meta-analysis. The additional data will narrow the confidence interval around the observed effect, allowing us to reject the null, reject the SESOI, or both. Analogous to the large sample sizes needed to detect small effects, a lot of data is needed to reject the SESOI when very narrow bounds are used for the equivalence test (e.g., $\Delta_{L} = -0.1$ and $\Delta_{U} = 0.1$).

>>>>

In order to distinguish between these possibilities, we can define what a “meaningful effect” (SESOI) would be and use it as the bounds for an equivalence test. If grades for this test were set at every `r printnum(sesoi * 100)`\% increase in correct answers (F = 0% to 6.25% ... A+ = 93.75% to 100%) we could decide that we are only interested in test differences that correspond to an increase or decrease of at least 1 grade point. Thus, our SESOI becomes a difference in raw scores of `r printnum(sesoi * 100)`\%, or `r printnum(sesoi, digits = 4)`. We can then perform the TOST procedure for a two-sample Welch’s *t*-test, using $\pm$ the SESOI of `r printnum(sesoi, digits = 4)` as the equivalence bounds ($\Delta$).
The TOST is non-significant, $t(`r printnum(Moon$TOST_df)`) = `r printnum(min(abs(c(Moon$TOST_t1, Moon$TOST_t2))))`$, $p = `r printp(max(Moon$TOST_p1, Moon$TOST_p2))`$ (Figure 2A). Thus, we cannot reject a true effect as large or larger than 6.25%.^[Because this is a replication of a study, it would have been reasonable to assume that we only want reject effects in the same direction as the effect in the original study. After all, much smaller effects may indicate non-replication, but so does large effects in the opposite direction. In that case, we would perform an inferiority test (see figure 1D) against $\Delta_{U}$. As can be seen in figure 2A, the $90\% CIs$ does not overlap with $\Delta_{U}$, so we can reject effects as large or larger than $`r printnum(sesoi)`$.] When results are neither statistically different from zero nor statistically equivalent, there is insufficient data to draw conclusions. Further studies are needed, which can be analyzed using a (small-scale) meta-analysis. The additional data will narrow the confidence interval around the observed effect, allowing us to reject the null, reject the SESOI, or both. Analogous to the large sample sizes needed to detect small effects, a lot of data is needed to reject the SESOI when very narrow bounds are used for the equivalence test (e.g., $\Delta_{L} = -0.1$ and $\Delta_{U} = 0.1$).
